%*******************************************************
% Acknowledgments
%*******************************************************
\refstepcounter{dummy}
\pdfbookmark[1]{Acknowledgments}{acknowledgments}

%\null
%\vspace{4\onelineskip}

%\fancyquote{Isaac Newton}{%
%    If I have seen further, it is by standing on the shoulders of giants.
%}

%\vspace{2\onelineskip}

\begingroup
\let\clearpage\relax

\section*{Acknowledgments}
Many people has had a hand in making this thesis, and deserves a large thanks.

% Supervisors
Thanks to my supervisors Brian Vinter and Kenneth Skovhede.
Brian Vinter was my main supervisor for the first year, and was responsible for establishing the contact to FOSS, and for giving me a good start. Kenneth Skovhede had to take over in the middle of the Summer, and without his support it would probably not have passed the finish line.

% Daily supervisors
I have had the pleasure of working with three daily supervisors.
Elisabeth Ulrikkeholm was my intial contact person at FOSS, and also served as the main supervisor from FOSS until December. I am grateful to her for introducing me to the people at FOSS.
Then Erik Dreier took over, and he had a massive influence on the project with artificial foreign objects.
I also appreciate the time he took to proof read this thesis, and for all the meetings.
From NBI's side I have been working closely with Carl-Johannes Johnsen during most of the project. 
I am grateful for the fact that you always had time to talk, even though you have been supervising $N$ other students. 
There is also no doubt that the thesis itself improved by your countless readings.

% Fellow students
It has been a long project and without the great collaboration at the eScience group it would have been a very bleak time indeed.
A great thanks to all the people involved.

% FOSS
I got an amazing reception at FOSS, and everyone has always been willing to help, and answer my emails. That played a large part in me feeling welcome, and kept the motivation up.

% Family and girlfriend.
Finally I have to thank my family and friends from outside the University for supporting me and keeping me sane.
A special thanks to my girlfriend Cilie for having to actually live with me during this, at times, stressing period. Furthermore, she also did large parts of the proof reading, often in the early iterations, and for that I am deeply grateful.

\endgroup